RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2014-12-05 manuscripts/manuscript.Rmd
formatting tweaks for 2.0.0

```{r}
phy <- get_trees_list(nex)
typeof(phy)
```

@@

```{r}
phy <- get_trees(nex)
plot(phy[[1]])
```

@@

```{r eval=FALSE}
tb_nex <- nexml_read("https://raw.github.com/rvosa/supertreebase/master/data/treebase/S100.xml")
tb_phy <- get_trees_list(tb_nex)
plot(tb_phy[[1]])
```

>>>>

```{r}
phy <- get_trees_list(nex)
class(phy)
```

@@

```{r fig.show="hide"}
phy <- get_trees(nex)
plot(phy[[1]]) 
```

@@

```{r eval=FALSE}
tb_nex <- nexml_read(
"https://raw.github.com/TreeBASE/supertreebase/master/data/treebase/S100.xml")
tb_phy <- get_trees_list(tb_nex)
```
